---
output: github_document
---

<!-- badges: start -->
  [![Codecov test coverage](https://codecov.io/gh/nfox29/steamReviews/branch/main/graph/badge.svg)](https://app.codecov.io/gh/nfox29/steamReviews?branch=main)
  <!-- badges: end -->


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
## steamReviews

The goal of this R package is to provide an accessible method for returning reviews from the Steam API into the R environment. The package can also be used to find information about the games, see the 

## Return all reviews for a game

The main function of the package is `allReviews`

The function is used to return every review of a game on the Steam store.

```{r eval = TRUE}
#library the package
library(steamReviews)

#Get reviews for Planet Zoo: Conservation Pack
reviews <- allReviews(game_id = 2013290)

#inspect reviews
head(reviews$review)
```
## Find a games ID

Most functions of the package require you to know the specific Steam store app id.

This can be found using the `gameID` function.

```{r eval = TRUE}
#library the package
library(steamReviews)

#Find game IDs for games containing the word "Halo"
ids <- gameID("Halo")

#inspect game IDs
head(ids)
```

## Issues and bugs

This package requires an internet connection as well as a connection to the Steam API, which may not be constantly available. 

If you discover a bug not associated with connection to the API that is not already a [reported issue](https://github.com/nfox29/steamReviews/issues), please [open a new issue](https://github.com/nfox29/steamReviews/issues/new) providing a reproducible example.

